---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bis620.2022

<!-- badges: start -->
[![R-CMD-check](https://github.com/YimingMiao/bis620.2022/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/YimingMiao/bis620.2022/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/YimingMiao/bis620.2022/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/YimingMiao/bis620.2022/actions/workflows/test-coverage.yaml)
[![Codecov test coverage](https://codecov.io/gh/YimingMiao/bis620.2022/branch/main/graph/badge.svg)](https://app.codecov.io/gh/YimingMiao/bis620.2022?branch=main)
[![lint](https://github.com/YimingMiao/bis620.2022/actions/workflows/lint.yaml/badge.svg)](https://github.com/YimingMiao/bis620.2022/actions/workflows/lint.yaml)
<!-- badges: end -->

The package `bis620.2022` contains the UKBiobank Accelerometry Data, and has functions to plot the time series and create spectral signatures by taking the modulus of Fourier coefficients of the channels.

[coverage page](https://app.codecov.io/gh/YimingMiao/bis620.2022?branch=main)

[lint result](https://github.com/YimingMiao/bis620.2022/actions/workflows/lint.yaml)

## Installation

You can install the development version of bis620.2022 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("YimingMiao/bis620.2022")
```

## Example

```{r message=FALSE}
library(bis620.2022)
```

This are some examples showing basic usage of the package:

Acquire data:

```{r}
data(ukb_accel)
```

Plot the time-series data:

```{r}
accel_plot(ukb_accel[1:1000,])
```

Plot the spectral signatures:

```{r}
ukb_accel[1:1000,] |>
  spectral_signature(take_log = FALSE) |>
  accel_plot()
```
